{{< var titll >}}

### 2024-11-14 docs/presentation.qmd
setup

## {{< var sec3.un1 >}}
```{r}
#| echo: false
#| output: false
apps <- appsn
```
{{< include tabpar.qmd >}}

## {{< var sec3.un2 >}}

@@

### Hybrid
```{r}
#| echo: false
#| output: false
apps <- apprh
```
{{< include tab.qmd >}}

@@

### Opposition
```{r}
#| echo: false
#| output: false
apps <- appro
```
{{< include tab.qmd >}}

# {{< var sec5.nmn >}}

@@

# {{< var sec6.nmn >}}

@@

## {{< var sec6.un1 >}}
```{r}
#| echo: false
#| output: false
apps <- appn1
```
{{< include tabpar.qmd >}}

## {{< var sec6.un2 >}}
```{r}
#| echo: false
#| output: false
apps <- appn2
```
{{< include tabpar.qmd >}}

## {{< var sec6.un3 >}}
```{r}
#| echo: false
#| output: false
apps <- appn2
```
{{< include tabpar.qmd >}}
## {{< var sec6.un4 >}}
```{r}
#| echo: false
#| output: false
apps <- appn4
```
{{< include tabpar.qmd >}}

# {{< var sec7.nmn >}}

## {{< var sec7.un1 >}}

# {{< var sec8.nmn >}}

@@

# {{< var sec9.nmn >}}

>>>>

## {{< var sec3.2.1 >}}
```{r}
#| echo: false
#| output: false
apps <- apsnn
```
{{< include tabpar.qmd >}}

## {{< var sec3.2.2 >}}

@@

### Hybrid
```{r}
#| echo: false
#| output: false
apps <- aprnn
```
{{< include tab.qmd >}}

@@

### Opposition
```{r}
#| echo: false
#| output: false
apps <- aprnn
```
{{< include tab.qmd >}}

# {{< var sec5.1 >}}

@@

# {{< var sec6.1 >}}

@@

## {{< var sec6.2.1 >}}
```{r}
#| echo: false
#| output: false
apps <- apn1n
```
{{< include tabpar.qmd >}}

## {{< var sec6.2.2 >}}
```{r}
#| echo: false
#| output: false
apps <- apn1n
```
{{< include tabpar.qmd >}}

## {{< var sec6.2.3 >}}
```{r}
#| echo: false
#| output: false
apps <- apn1n
```
{{< include tabpar.qmd >}}
## {{< var sec6.2.3 >}}
```{r}
#| echo: false
#| output: false
apps <- apn1n
```
{{< include tabpar.qmd >}}

# {{< var sec8.1 >}}

@@
